Delayed effects of climate on vital rates lead to demographic divergence in Amazonian forest fragments

### 2021-06-23 doc/paper.Rmd
added citations to r packages

All analyses were conducted in `r version$version.string` [@rcoreteamLanguageEnvironmentStatistical2020].

>>>>

All analyses were conducted in `r version$version.string` [@rcoreteamLanguageEnvironmentStatistical2020] using the `targets` package for workflow management [@landauTargetsPackageDynamic2021].
Figures were created with the aid of the `gratia`, `ggplot2`, and `patchwork` packages [@wickhamGgplot2ElegantGraphics2016; @simpsonGratiaGracefulGgplot2021; @pedersenPatchworkComposerPlots2020].
